get_gold_set_images

### 2018-01-11 analysis-validation/mtcnn_evaluation.Rmd
validation code

---
title: "mtcnn evaluation"
output: html_notebook
---

@@

Load data
```{r, message=FALSE, warning=FALSE}
setwd("..")

data <- read_csv("data/final_output/mtcnn3.csv") %>%
  distinct(video, frame, .keep_all = TRUE)

@@

p <- score[4,2] / (score[4,2] + score[2,2])
r <- score[4,2] / (score[4,2] + score[1,2])
f <- 2 * p * r / (p + r)
```

>>>>

---
title: "mtcnn evaluation"
output: html_document
---

@@

Load data
```{r, message=FALSE, warning=FALSE}
setwd("..")
data <- read_csv("data/final_output/mtcnn3.csv") %>%
  distinct(video, frame, .keep_all = TRUE)

@@

p <- score[4,2] / (score[4,2] + score[2,2])
r <- score[4,2] / (score[4,2] + score[1,2])
f <- 2 * p * r / (p + r)

print(paste("P:", round(p,3), "R:", round(r,3), "F:", round(f,3)))
```

### 2018-01-11 scripts/ground_truth_creation/get_gold_set_images.Rmd
validation code

Sample high density faces, remove selected from original data
```{r}
high_density_faces_sample <- data %>%
  group_by(video) %>%
  filter(is_face == "True") %>%
  sample_n(7)

@@

Choose random frames from remaining
```{r}
random_sample <- data %>%
  group_by(video) %>%
  sample_n(7)
```

>>>>

Sample high density faces, remove selected from original data
```{r}
high_density_faces_sample <- data %>%
  group_by(video) %>%
  filter(is_face == "True") %>%
  sample_n(7) %>%
  mutate(sample_type = "high_density")

@@

Choose random frames from remaining
```{r}
random_sample <- data %>%
  group_by(video) %>%
  sample_n(7) %>%
  mutate(sample_type = "random")
```
